A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-06-14 bioc-workflow.Rmd
update superscript to mardown format

As a use-case, we analyse a recent high-throughput spatial proteomics
dataset from pluripotent mouse embryonic stem cells (E14TG2a)
[@hyper]. The data was generated using hyperplexed LOPIT (hyperLOPIT),
an improved method relying on improved sub-cellular fractionation and
more accurate quantitation, leading to more reliable classification of
protein localisation across the whole sub-cellular space. The method
uses an elaborate sub-cellular fractionation scheme, enabled by the
use of Tandem Mass Tag (TMT) [Thompson:2003] 10-plex and application
of the MS data acquisition technique named synchronous precursor
selection MS$^3$ (SPS-MS$^3$) [@McAlister:2014], for TMT
quantification with high accuracy and precision. Three biological
replicates were generated from the E14TG2a experiment, the first was
to target low density fractions and the second and third were to
emphasis separation of the denser organelles.  The intersect of
replicates 1 and 2 was treated as a 20-plex dataset for the analysis
discussed in the manuscript [@hyper] as it has been shown that
combining replicates across from different gradients can increase
spatial resolution [@Trotter:2010]. The combination of replicates resulted
in 5032 proteins common in both experiments.

>>>>

As a use-case, we analyse a recent high-throughput spatial proteomics
dataset from pluripotent mouse embryonic stem cells (E14TG2a)
[@hyper]. The data was generated using hyperplexed LOPIT (hyperLOPIT),
an improved method relying on improved sub-cellular fractionation and
more accurate quantitation, leading to more reliable classification of
protein localisation across the whole sub-cellular space. The method
uses an elaborate sub-cellular fractionation scheme, enabled by the
use of Tandem Mass Tag (TMT) [Thompson:2003] 10-plex and application
of the MS data acquisition technique named synchronous precursor
selection MS^3^ (SPS-MS^3^) [@McAlister:2014], for TMT
quantification with high accuracy and precision. Three biological
replicates were generated from the E14TG2a experiment, the first was
to target low density fractions and the second and third were to
emphasis separation of the denser organelles.  The intersect of
replicates 1 and 2 was treated as a 20-plex dataset for the analysis
discussed in the manuscript [@hyper] as it has been shown that
combining replicates across from different gradients can increase
spatial resolution [@Trotter:2010]. The combination of replicates resulted
in 5032 proteins common in both experiments.
